The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Radio Observatory Long Wavelength Array

### 2018-02-05 paper.tex
minor fixes in wording

The key advantage of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the linear
size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$
because each block can be manipulated independently of the other blocks. This computational savings
is what makes this matrix algebra approach to interferometric imaging feasible.

@@

The noise in each map is empirically measured using jackknife resampling. The dataset is first split
into even- and odd-numbered integrations. These two groups are then imaged and CLEANed
independently, before being compared against the maps constructed from all of the available data
using the standard jackknife variance estimator. This estimate of the variance includes all sources
of error that operate on $\sim13$ second timescales (the integration time) such as thermal noise and
rapid ionospheric fluctuations, but does not account for more slowly varying effects (for example,
sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
noise $<900$ mJy and therefore each map is likely at or near the confusion limit.

>>>>

The key advantage of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}. The computational complexity of many common matrix
operations (eg. solving a linear system of equations) is $\mathcal{O}(N^3)$, where $N$ is the linear
size of the matrix.  By splitting the equation into $M$ independent blocks, the number of floating
point operations required to solve the linear system of equations is now $\mathcal{O}(N^3M^{-2})$,
because each block can be manipulated independently of the other blocks. This computational savings
is what makes this matrix algebra approach to interferometric imaging feasible. For the dataset
presented in this paper, computing the elements of the transfer matrix takes $\sim$10 hours per
frequency channel on a 10-node cluster, but once the matrix has been computed the imaging process
described in \S\ref{sec:mmode-imaging} takes $\sim$10 minutes, and the deconvolution process
described in \S\ref{sec:clean} was allowed to run for $\sim$10 hours.

@@

The noise in each map is empirically measured using jackknife resampling. The dataset is first split
into even- and odd-numbered integrations. These two groups are then imaged and CLEANed
independently, before being compared against the maps constructed from all of the available data
using the jackknife standard error estimator. This estimate of the standard error includes all
sources of error that operate on $\sim13$ second timescales (the integration time) such as thermal
noise and rapid ionospheric fluctuations, but does not account for more slowly varying effects (for
example, sidereal variation in the system temperature or day-night fluctuations in the ionosphere).
These noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
noise $<900$ mJy and therefore each map is likely at or near the confusion limit.
